The guts of the dispRity package

### 2021-01-27 inst/gitbook/06_guts.Rmd
added n.subsets function

@@

## The `dispRity` object content

>>>>

#### `n.subsets`

This function simply counts the number of subsets in a `dispRity` object.

```{r}
## How many subsets are in this object?
n.subsets(disparity)
```

#### `size.subsets`

This function tells the number of elements in each subsets of a `dispRity` object.

```{r}
## How many elements are there in each subset?
size.subsets(disparity)
```

@@

## The `dispRity` object content {#disprity-object}
